Data preparation

### 2020-10-02 production/prod_prep-data.rmd
reunion 2-10

- Recode NAs

@@

@@

### Recode sex
sex_plotbefore <- sjPlot::plot_frq(indepvar$sex, title ="Gender before")
indepvar$sex=ifelse(indepvar$sex==1,0,ifelse(indepvar$sex==2,1,NA))  
sex_plotafter <- sjPlot::plot_frq(indepvar$sex, title ="Gender after")

@@

### Recode Age
  # Age
agebefore<-sjPlot::plot_frq(indepvar$age, title = "Age before",show.mean = T , show.values = F,show.n = F, axis.labels = NULL, type = c("histogram"))

@@

ageafter <- sjPlot::plot_frq(indepvar$age_c, title = "Age after", show.na = T, axis.labels =   c("18-25","25 -35", "35-45", "45-55", "55,65", "65-85","NA(>85)"))

@@

degreafter<- sjPlot::plot_frq(indepvar$univ, coord.flip = TRUE, title = "Dummy university")

@@

# Ahora dividir el vector income por n° de personas en hogar
indepvar$hhincome=indepvar$income/indepvar$hompop
summary(indepvar$hhincome)

@@

sjPlot::plot_frq(indepvar$quintile_miss, coord.flip = TRUE, title = "Quintiles de ingreso" , axis.labels=c("quintile 1","quintile 2","quintile 3","quintile 4","quintile 5","Miss"))
#stargazer(indepvar$quintile_miss, type = "html")

@@

movestatusbefore <- sjPlot::plot_frq(indepvar$movstatus, coord.flip = TRUE, title = "Subjective status mobility before")

@@

indepvar$movstatus <- set_labels(indepvar$movstatus,labels = c("Sin movilidad"=1,
                                                                "Mov. Ascendente"=2,
                                                                    "Mov. Descendente"=3,
                                                                    "Indeterminado"=4))

movestatusafter <- sjPlot::plot_frq(indepvar$movstatus, coord.flip = TRUE, title = "subjective status mobility after")     
cowplot::plot_grid(movestatusbefore, movestatusafter, ncol=2)
```

@@

```{r}
sjPlot::plot_likert(detearn[, 3:8],
                    geom.colors   = c("#9ecae1", "#6baed6", "#4292c6", "#2171b5"), # colorbrewer2.org
                    cat.neutral = 3,
                    sort.frq      = "neg.asc", # sort descending)
                    title         = "Before detearn",
                    intercept.line.color = "white", # vertical middle
                    expand.grid   = F, # no inner margins in plot
                    show.n        = FALSE, # hide N's in axis labels
                    grid.range    = 1.8,
                    geom.size = 0.6) # expand axis 130% ))

@@

sjPlot::plot_likert(detearn[,3:8],
                    geom.colors   = c("#9ecae1", "#6baed6", "#4292c6", "#2171b5"), # colorbrewer2.org
                    cat.neutral = 3,
                    sort.frq      = "neg.asc", # sort descending)
                    title         = "After detearn",
                    intercept.line.color = "white", # vertical middle
                    expand.grid   = F, # no inner margins in plot
                    show.n        = FALSE, # hide N's in axis labels
                    grid.range    = 1.8,
                    geom.size = 0.6) # expand axis 130% ))

freq(detearn$respons)
```

@@

@@

  # Estimación del modelo c/ unmerit 2do orden
cfa_perpref2 <- '
	  # latent variables
	  merit =~ hwork + ambition
	  parent=~ wealthy + pareduc
	  backg=~ race + gender
		network=~ people + polcone
		unmerit=~ parent + backg + network # 2nd order
	  bmerit =~ welljob + hardjob
	  need=~ family + child
	  '
fit_perpref2 <- cfa(cfa_perpref2, data = merit_per_pref,missing = "ML")
#	  summary(fit_perpref2, fit.measures=TRUE,standardized=TRUE)
  # Path model
		  semPaths(fit_perpref2,layout = "tree", rotation = 2,
		  	intercepts = FALSE, style = "lisrel", curvePivot = TRUE,
		  	sizeMan = 3.5, sizeLat = 6)
```

@@

@@

Bases de datos creadas.

[Explicar mejor]

Indepvar.rda: variables sociodemograficas
redistrib_sco: variables latentes de preferencias redistributivas.
merit_perc_pref_sco: variables latentes de creencias meritocraticas.

## Merge varaibles indivuales.

@@

## 2.1: SWIID
```{r}
# Inequality swiid (4)        
#load(url("https://raw.githubusercontent.com/franciscomeneses/bases/master/swiid8_3.rda"))
load("input/data/original/swiid8_3.rda")

@@

# Continuo
swiid_summary09$v5=countrycode(swiid_summary09$.dots...country,'country.name','iso3n')
str(swiid_summary09$v5)

# Categórico
swiid_summary09$v5c=countrycode(swiid_summary09$.dots...country,'country.name','iso3c')
str(swiid_summary09$v5c)

@@

```{r}
### Recode Age
  # Age
redistributionswiid <- hist(mer_pref$redis_relativo)
summary(mer_pref$redis_relativo)
redistribbradley <- hist(mer_pref$redis_bradley)

cowplot::plot_grid(redistributionswiid, redistribbradley, ncol=1)

## 2.2: Qog

```{r echo=FALSE, results='hide'}
#Para descargar

@@

__Economic fredom variable description:__ The index is founded upon objective components that reflect the presence (or absence) of economic freedom. The index comprises 21 components designed to identify the consistency of institutional arrangements and policies with economic freedom in five major areas: size of government (fi_sog), legal structure and security of property rights (fi_legprop), access to sound money (fi_sm), freedom to trade internationally (fi_ftradeint), regulation of credit, labor and business (fi_reg). The index ranges from 0-10 where 0 corresponds to ``less economic freedom'' and 10 to ``more economic freedom''. This is the version of the index published at the current year of measurement, without taking methodological changes over time into account.

@@

## Pib per capita

@@

Taiwán no posee información sobre pibpc en el banco mundial, por ende el pib per capita para este pais se obtuvo de otra fuente: [DatosMacro](https://datosmacro.expansion.com/pib/taiwan)

@@

## Government Effectivinnes

@@

sjPlot::plot_frq(mer_pref$goveffect, title = "Government Effectivinnes",show.mean = T , show.values = F,show.n = F, axis.labels = NULL, type = c("histogram"))
```

(Banco Mundial)[https://databank.bancomundial.org/databases/governance-effectiveness]

La efectividad del gobierno captura las percepciones de la calidad de los servicios públicos, la calidad del servicio civil y el grado
de su independencia de las presiones políticas, la calidad de la formulación e implementación de políticas, y la credibilidad de la
compromiso del gobierno con tales políticas. Más información [aquí](https://info.worldbank.org/governance/wgi/pdf/ge.pdf)

>>>>

- Recode NAs (9)

@@

 - generate 5 multiple complete datasets
 - fit model for each complete dataset
 - predict scores for all model
 - compute 'average' across 5 sets of scores

@@

### Recode sex
sex_plotbefore <- sjPlot::plot_frq(indepvar$sex, title ="Gender before") + xlab("Sex")

indepvar$sex=ifelse(indepvar$sex==1,0,ifelse(indepvar$sex==2,1,NA))

sex_plotafter <- sjPlot::plot_frq(indepvar$sex, title ="Gender after") + xlab("Sex")

@@

### Recode Age
  # Age
agebefore<-sjPlot::plot_frq(indepvar$age, title = "Age before",show.mean = T , show.values = F,show.n = F, axis.labels = NULL, type = c("histogram")) + xlab("Age")

@@

ageafter <- sjPlot::plot_frq(indepvar$age_c, title = "Age after", show.na = T, axis.labels =   c("18-25","25 -35", "35-45", "45-55", "55,65", "65-85","NA(>85)")) + xlab("Age")

@@

degreafter<- sjPlot::plot_frq(indepvar$univ, coord.flip = TRUE, title = "Dummy university") + xlab("University education")

@@

# Ahora dividir el vector income por n° de personas en hogar
indepvar$hhincome=indepvar$income/indepvar$hompop
#summary(indepvar$hhincome)

@@

sjPlot::plot_frq(indepvar$quintile_miss, coord.flip = TRUE, title = "income quintiles" , axis.labels=c("quintile 1","quintile 2","quintile 3","quintile 4","quintile 5","Miss")) + xlab("Income quintiles")

#stargazer(indepvar$quintile_miss, type = "html")

@@

movestatusbefore <- sjPlot::plot_frq(indepvar$movstatus, coord.flip = TRUE, title = "Subjective Mobility before")

@@

indepvar$movstatus <- set_labels(indepvar$movstatus,labels = c("No mobility"=1,
                                                                "Upward mobility"=2,
                                                                    "Upward mobility"=3,
                                                                    "Indeterminate"=4))

movestatusafter <- sjPlot::plot_frq(indepvar$movstatus, coord.flip = TRUE, title = "Subjective mobility after")     
cowplot::plot_grid(movestatusbefore, movestatusafter, ncol=2) + xlab("Subjective status mobility")
```

@@

```{r}
before_detearn<-sjPlot::plot_likert(detearn[,3:8],
                    geom.colors   = c("#9ecae1", "#6baed6", "#4292c6", "#2171b5"), # colorbrewer2.org
                    cat.neutral = 3,
                    sort.frq      = "neg.asc", # sort descending)
                    title         = "Before detearn",
                    intercept.line.color = "white", # vertical middle
                    expand.grid   = F, # no inner margins in plot
                    show.n        = FALSE, # hide N's in axis labels
                    grid.range    = 1.8,
                    geom.size = 0.6) # expand axis 130% ))

save(before_detearn, file="output/images/before_detearn.png")

```{r}

@@

after_detearn<- sjPlot::plot_likert(detearn[,3:8],
                    geom.colors   = c("#9ecae1", "#6baed6", "#4292c6", "#2171b5"), # colorbrewer2.org
                    cat.neutral = 3,
                    sort.frq      = "neg.asc", # sort descending)
                    title         = "After detearn",
                    intercept.line.color = "white", # vertical middle
                    expand.grid   = F, # no inner margins in plot
                    show.n        = FALSE, # hide N's in axis labels
                    grid.range    = 1.8,
                    geom.size = 0.6) # expand axis 130% ))

save(after_detearn, file="output/images/after_detearn.png")

@@

 - 
Estimation of the model c / unmerit 2nd order
 - 
Estimation of the model c / unmerit 2nd order

-

@@

  # Estimation of the model c / unmerit 2nd order
cfa_perpref2 <- '
	  # latent variables
	  merit =~ hwork + ambition
	  parent=~ wealthy + pareduc
	  backg=~ race + gender
		network=~ people + polcone
		unmerit=~ parent + backg + network # 2nd order
	  bmerit =~ welljob + hardjob
	  need=~ family + child
	  '
fit_perpref2 <- cfa(cfa_perpref2, data = merit_per_pref,missing = "ML")
#	  summary(fit_perpref2, fit.measures=TRUE,standardized=TRUE)
  # Path model
		  semPaths(fit_perpref2,layout = "tree", rotation = 2,
		  	intercepts = FALSE, style = "lisrel", curvePivot = TRUE,
		  	sizeMan = 3.5, sizeLat = 6)
```

@@

 - generate 5 multiple complete datasets
 - fit model for each complete dataset
 - predict scores for all model
 - compute 'average' across 5 sets of scores
 - Generate factor scores

@@

In this section, 3 databases were created on sociodemographic variables, dependent latent variables (Redistributive preferences) and independent latent variables (Meritocratic beliefs).

Each one is indicated below and later they are unified.

Indepvar.rda: sociodemografic variables 
redistrib_sco: latent variables of redistributive preferences.
merit_perc_pref_sco: latent variables of meritocratic beliefs.

## Merge variables indivuales.

@@

## 2.1: Standardized World Income Income Inequality Database (SWIID)
```{r}
# Inequality swiid (4)        
#load(url("https://raw.githubusercontent.com/franciscomeneses/bases/master/swiid8_3.rda"))
load("input/data/original/swiid8_3.rda")

@@

# Continuous variable

swiid_summary09$v5=countrycode(swiid_summary09$.dots...country,'country.name','iso3n')
str(swiid_summary09$v5)

# categorical variables

swiid_summary09$v5c=countrycode(swiid_summary09$.dots...country,'country.name','iso3c')
str(swiid_summary09$v5c)

@@

Two ways of calculating the redistribution variable at the country level are presented below. Both proportionally equivalent.
   - Calculation according to Bradley[(2003)](https://www.jstor.org/stable/25054218?seq=1) __(net gini / gini mkt)*100__
   - Calculation used by Solt in [SWIID](https://fsolt.org/swiid/) __(gini mkt - gini net)/gini mkt__

```{r }
### Recode Age
  # Age 
hist1 <- mer_pref %>% ggplot(aes(x=redis_relativo)) + geom_histogram() + xlab("Redistribution")
hist2 <- mer_pref %>% ggplot(aes(x=redis_bradley)) + geom_histogram() + xlab("Redistribution")
ggsave(plot_grid(list(hist1, hist2), tags = c("Bradley", "Solt")),  file ="output/images/redistriv_comparation.png")
```

![](../output/images/redistriv_comparation.png)

## 2.2:  Quality of Government (QoG)

 - to download the database from your quote on github

```{r echo=FALSE, results='hide'}
# to download the database from your quote on github

@@

__Economic fredom variable description:__ The index is founded upon objective components that reflect the presence (or absence) of economic freedom. The index comprises 21 components designed to identify the consistency of institutional arrangements and policies with economic freedom in five major areas: size of government (fi_sog), legal structure and security of property rights (fi_legprop), access to sound money (fi_sm), freedom to trade internationally (fi_ftradeint), regulation of credit, labor and business (fi_reg). The index ranges from 0-10 where 0 corresponds to less economic freedom and 10 to more economic freedom. This is the version of the index published at the current year of measurement, without taking methodological changes over time into account.

- Merge

@@

```{r}
sjPlot::plot_frq(mer_pref$fi_index, title = "Pib Per capita",show.mean = T , show.values = F,show.n = F, axis.labels = NULL, type = c("histogram")) +xlab("Economic freedom")
```

# Data Ban

Country data on their wealth and government effectiveness were obtained from World Bank data sets. This institution has an extensive set of data and a platform to facilitate its accessibility, which you can access [here](https://datos.bancomundial.org/).

## GDP per capita (current US $)

To access the data click [here](https://datos.bancomundial.org/indicador/NY.GDP.PCAP.CD)

@@

Taiwan does not have information on GDP in the world bank, therefore the GDP per capita for this country was obtained from another source: [DatosMacro](https://datosmacro.expansion.com/pib/taiwan)

@@

## Government effectiveness

@@

sjPlot::plot_frq(mer_pref$goveffect, title = "government effectiveness",show.mean = T , show.values = F,show.n = F, axis.labels = NULL, type = c("histogram")) + xlab("Government effectiveness")
```

[World Bank](https://databank.bancomundial.org/databases/governance-effectiveness)

Government effectiveness captures perceptions of the quality of public services, the quality of civil service, and the degree
its independence from political pressures, the quality of policy formulation and implementation, and the credibility of the
government commitment to such policies. More information [here](https://info.worldbank.org/governance/wgi/pdf/ge.pdf)
